---
title: "Insurance Lists Review"
output: word_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
options(digits = 2)

INS_Check <- read_xlsx("C:\\Users\\USER\\Desktop\\WORK CURRENT\\Insurance - THE REINSURING\\3PL INSURANCE CHECK.xlsx", sheet = "Comparison Table")
INS_Check <- INS_Check %>% mutate(Status = ifelse(str_detect(Status,regex("active",ignore_case = T)),"ACTIVE",Status)) %>% filter(Status == "ACTIVE")
colnames(INS_Check) <- colnames(INS_Check) %>% str_replace_all(.," ","_")
```

# Total Counts

**Total number of Employees:** `r nrow(INS_Check)`

**Employee Files**

The Total number of Active employees with files at the HQ is `r INS_Check %>% summarise(sum(File_Present)) %>% pull()` or `r INS_Check %>% summarise(mean(File_Present)) %>% pull() *100` % of the total.

Therefore the number of employees who have not submitted any files is `r INS_Check %>% summarise(sum(!File_Present)) %>% pull()` or `r INS_Check %>% summarise(mean(!File_Present)) %>% pull()` % of the total.

Broken Down by  Company
```{r file not present, echo=FALSE}
INS_Check %>% group_by(Company) %>% summarise(sum(!File_Present),mean(!File_Present)*100) %>% knitr::kable(col.names = c("Company","Count","% of Company Total"))
```

Below is the list of names broken down by company

2B:
```{r f not present 2B, echo=FALSE}
INS_Check %>% filter(!File_Present, Company == "2B") %>% select(ID,Name) %>% knitr::kable(align = c("l","r"))
```

BAPCO:
```{r f not present BAPCO, echo=FALSE}
INS_Check %>% filter(!File_Present, Company == "BAPCO") %>% select(ID,Name) %>% knitr::kable()
```

PETCO:
```{r f not present PETCO, echo=FALSE}
INS_Check %>% filter(!File_Present, Company == "PETCO") %>% select(ID,Name) %>% knitr::kable()
```

Sharif:
```{r f not present SHARIF, echo=FALSE}
INS_Check %>% filter(!File_Present, Company == "SHARIF") %>% select(ID,Name) %>% knitr::kable()
```

Rawat:
```{r f not present RAWAT, echo=FALSE}
INS_Check %>% filter(!File_Present, Company == "RAWAT") %>% select(ID,Name) %>% knitr::kable()
```

**Names received from Al Mutakhasisa:**

The total number of employees whose names were recieved from Al Mutakhasisa is `r INS_Check %>% summarise(sum(Incoming)) %>% pull()` or `r INS_Check %>% summarise(mean(Incoming)) * 100` % of the total.

Broken Down by Company:

```{r incoming-company, echo=FALSE}
INS_Check %>% group_by(Company) %>% summarize(sum(Incoming),mean(Incoming)*100) %>% knitr::kable(col.names = c("Company","Count","% of Company Total"))
```

Broken down by Batches:

```{r by batches incoming, echo=FALSE}
INS_Check %>%  group_by(Incoming_Batch) %>% summarize(Count = sum(Incoming)) %>% filter(!is.na(Incoming_Batch)) %>% knitr::kable(col.names = c("Batch","Count"),align = c("l","r"))
```

**Names on our checklists**

The total number of employees whose names were sent by us; excluding the untracked first batch, `r INS_Check %>%  summarise(sum(Outgoing)) %>% pull()` or `r INS_Check %>%  summarise(mean(Outgoing)) %>% pull() * 100` % of the total.

Broken Down by Company:

```{r outgoing-company, echo=FALSE}
INS_Check %>%  group_by(Company) %>% summarize(sum(Outgoing),mean(Outgoing)*100) %>% knitr::kable(col.names = c("Company","Count","% of the Company Total"))
```

Broken down by Batches:

```{r by batches outgoing, echo=FALSE}
INS_Check %>%  group_by(Outgoing_Batch) %>% summarize(Count = sum(Outgoing)) %>% filter(!is.na(Outgoing_Batch)) %>% knitr::kable(col.names = c("Batch","Count"),align = c("l","r"))
```


# Employees with issues:


**Names who have files but don't appear on any lists, presumably because they have not been sent:**

The total number of employees who have files but don't appear on any list is `r INS_Check %>%  summarise(sum(File_Present_but_not_in_Outgoing_or_incoming)) %>% pull()` or `r INS_Check %>%  summarise(mean(File_Present_but_not_in_Outgoing_or_incoming)) %>% pull() * 100` % of the total.

Broken Down by Company:
```{r not included anywhere, echo=FALSE}
INS_Check %>% group_by(Company) %>%  summarise(sum(File_Present_but_not_in_Outgoing_or_incoming),mean(File_Present_but_not_in_Outgoing_or_incoming)*100) %>% knitr::kable(col.names = c("Company","Count","% of Company Total"))
```

Below is the list of Names broken down by company

2B:

```{r table of not included anywhere 2B, echo=FALSE}
INS_Check %>%  filter(File_Present_but_not_in_Outgoing_or_incoming == TRUE, Company == "2B") %>% select(ID,Name) %>% knitr::kable()
```

BAPCO:

```{r table of not included anywhere BAPCO, echo=FALSE}
INS_Check %>%  filter(File_Present_but_not_in_Outgoing_or_incoming == TRUE, Company == "BAPCO") %>% select(ID,Name) %>% knitr::kable()
```

PETCO:

```{r table of not included anywhere PETCO, echo=FALSE}
INS_Check %>%  filter(File_Present_but_not_in_Outgoing_or_incoming == TRUE, Company == "PETCO") %>% select(ID,Name) %>% knitr::kable()
```

Sharif:

```{r table of not included anywhere SHARIF, echo=FALSE}
INS_Check %>%   filter(File_Present_but_not_in_Outgoing_or_incoming == TRUE, Company == "SHARIF") %>% select(ID,Name) %>% knitr::kable()
```

Rawat:

```{r table of not included anywhere RAWAT, echo=FALSE}
INS_Check %>%  filter(File_Present_but_not_in_Outgoing_or_incoming == TRUE, Company == "Rawat") %>% select(ID,Name) %>% knitr::kable()
```


**Names that appear on our lists but not in Al Mutakhasisa's lists, presumably because they were lost/not processed by Al Mutakhasisa:**


The Total number of employees who appear on our list but not Al Mutakhasisa's is `r INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>%  summarise(sum(Included_in_Outgoing_not_Incoming)) %>% pull()` or  `r INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>%  summarise(mean(Included_in_Outgoing_not_Incoming)) %>% pull() * 100` % of the total.

Broken down by Company:

```{r out not in breakdown, echo=FALSE, warning=FALSE}
INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>% group_by(Company) %>% summarise(Count = sum(Included_in_Outgoing_not_Incoming)) %>% knitr::kable()
```

Below is the list of Names broken down by company

2B:

```{r out but not in 2B, echo=FALSE, warning=FALSE}
INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>%  filter(Included_in_Outgoing_not_Incoming == TRUE, Company == "2B") %>% select(ID,Name) %>% knitr::kable()
```

BAPCO:

```{r out but not in BAPCO, echo=FALSE, warning=FALSE}
INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>%  filter(Included_in_Outgoing_not_Incoming == TRUE, Company == "BAPCO") %>% select(ID,Name) %>% knitr::kable()
```

PETCO:

```{r out but not in PETCO, echo=FALSE, warning=FALSE}
INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>%  filter(Included_in_Outgoing_not_Incoming == TRUE, Company == "PETCO") %>% select(ID,Name) %>% knitr::kable()
```

Sharif:

```{r out but not in SHARIF, echo=FALSE, warning=FALSE}
INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>%  filter(Included_in_Outgoing_not_Incoming == TRUE, Company == "SHARIF") %>% select(ID,Name) %>% knitr::kable()
```

Rawat:

```{r out but not in RAWAT, echo=FALSE, warning=FALSE}
INS_Check %>% filter(Outgoing_Batch <= max(as.numeric(Incoming_Batch),na.rm = T)) %>%  filter(Included_in_Outgoing_not_Incoming == TRUE, Company == "SHARIF") %>% select(ID,Name) %>% knitr::kable()
```

**Names that appear on the incoming lists from Al Mutakhasisa but have not collected their insurance cards:**

***NOTE:*** We do not have a complete picture of which employees have recieved their cards with information available for only `r INS_Check %>% filter(Delivered != "#N/A") %>% nrow(.)`. 

The total number of employees who should have ready cards and are confirmed not to have recieved them is `r INS_Check %>%  summarise(sum(Included_in_Incoming_but_not_Delivered,na.rm = T)) %>% pull()`.


